Different creatures in the R zoo

### 2024-08-04 text/14/axis.Rmd
Fixed tags

---
title: "Some simple examples of manipulating the axes in a graph"
author: "Steve Simon"
source: "http://www.pmean.com/axis.html"
date: "2014-01-01"
category: Blog post
tags:
- Data visualization
- Rmarkdown graphs
output: html_document
page_update: partial
---

>>>>

---
title: "Some simple examples of manipulating the axes in a graph"
author: "Steve Simon"
source: "http://www.pmean.com/axis.html"
date: "2014-01-01"
categories: Blog post
tags:
- Data visualization
- Rmarkdown graphs
output: html_document
page_update: partial
---

### 2024-08-04 text/15/difference-of-two-exponentials.Rmd
Fixed tags

---
title: "Nonlinear regression for the difference of two exponentials"
author: "Steve Simon"
source: "http://blog.pmean.com/difference-of-two-exponentials/"
date: "2015-10-05"
category: 
- Blog post
tags:
- incomplete page
- nonlinear regression
- R software
- Rmarkdown graphs
output: html_document
page_update: complete
---

>>>>

---
title: "Nonlinear regression for the difference of two exponentials"
author: "Steve Simon"
source: "http://blog.pmean.com/difference-of-two-exponentials/"
date: "2015-10-05"
categories: 
- Blog post
tags:
- incomplete page
- nonlinear regression
- R software
- Rmarkdown graphs
output: html_document
page_update: complete
---

### 2024-08-04 text/22/definition-schoenfeld-residuals.Rmd
Fixed tags

---
title: "Schoenfeld residuals"
author: "Steve Simon"
date: '2022-11-30'
output:
  html_document: default
category: Blog post
tags:
- Rmarkdown code
- Survival analysis
source: new
page_update: complete
---

>>>>

---
title: "Schoenfeld residuals"
author: "Steve Simon"
date: '2022-11-30'
output:
  html_document: default
categories: Blog post
tags:
- Rmarkdown code
- Survival analysis
source: new
page_update: complete
---

### 2024-08-04 text/22/dunnetts-test.Rmd
Fixed tags

---
title: "Dunnett's test"
author: "Steve Simon"
date: '2022-07-04'
output:
  html_document: default
category: Blog post
tags:
- Analysis of means
- Rmarkdown graphs
source: new
page_update: complete
---

>>>>

---
title: "Dunnett's test"
author: "Steve Simon"
date: '2022-07-04'
output:
  html_document: default
categories: Blog post
tags:
- Analysis of means
- Rmarkdown graphs
source: new
page_update: complete
---

### 2024-08-04 text/22/posix-time.Rmd
Fixed tags

---
title: "The POSIX time standard"
author: "Steve Simon"
date: "2022-11-12"
output:
  html_document: default
category: Blog post
tags:
- Data science
- Rmarkdown code
source: new
page_update: complete
---

>>>>

---
title: "The POSIX time standard"
author: "Steve Simon"
date: "2022-11-12"
output:
  html_document: default
categories: Blog post
tags:
- Data science
- Rmarkdown code
source: new
page_update: complete
---

### 2024-08-04 text/22/r-creatures.Rmd
Fixed tags

---
title: "Different creatures in the R zoo"
author: "Steve Simon"
source: new
date: "2022-04-14"
category: 
- Blog post
tags:
- R software
- Rmarkdown code
output: html_document
page_update: complete
---

>>>>

---
title: "Different creatures in the R zoo"
author: "Steve Simon"
source: new
date: "2022-04-14"
categories: 
- Blog post
tags:
- R software
- Rmarkdown code
output: html_document
page_update: complete
---
